Composable Concurrency Models

### 2016-11-19 slides/slides.tex
Added numbering to table of contents
Made some last-minute changes

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{snakes}

% this actually isn't totally hideous:
\usetheme[numbering=counter, progressbar=frametitle, sectionpage=none]{metropolis}
\setbeamertemplate{bibliography item}[text]
\setbeamertemplate{frametitle continuation}{}

@@

    If $A \rightarrow B$ and $B \rightarrow C$, then $A \rightarrow C$.

@@

  \begin{frame}
    \frametitle{Possible conflicts}
    \centering
    \small

@@

    \vfill
    \begin{tabular}{c | c c c c | c c c c}
      & \multicolumn{4}{c|}{\textbf{Safety}} & \multicolumn{4}{|c}{\textbf{Liveness}} \\
      & atoms & refs & agents & channels & atoms & refs & agents & channels \\
      \hline
      atoms & \n & \n & \n & \n & \y & \y & \y & \n \\
      refs & \n & \y & \y & \n & \y & \y & \y & \n \\
      agents & \y & \y & \y & \y & \y & \y & \y & \n \\
      channels & \y & \y & \y & \y & \y & \y & \n & \n
    \end{tabular}
    \vfill
    \begin{itemize}
      \onslide<2->{
        \item A model reexecutes code that performs an irrevocable action.
      }
      \onslide<3->{
        \item A model reexecutes code that causes the reexecution to continually happen.
      }
      \onslide<4->{
        \item A model that supports blocking operations is used within a model that doesn't.
      }
      \onslide<5->{
        \item A model does not guarantee safety or liveness by design.
      }
    \end{itemize}
  \end{frame}

>>>>

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{color}
\usepackage{colortbl}
\usepackage{diagbox}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{snakes}

\defbeamertemplate{section in toc}{numbered titles}{%
  \leavevmode
  \parbox[t]{1.5em}{\inserttocsectionnumber.}%
  \parbox[t]{\dimexpr\textwidth-1em\relax}{\inserttocsection}\par
}

\defbeamertemplate{subsection in toc}{indented titles}{%
  \leavevmode
  \parbox[t]{3em}{\hfill}%
  \parbox[t]{\dimexpr\textwidth-1em\relax}{\inserttocsubsection}\par
}

% this actually isn't totally hideous:
\usetheme[numbering=counter, progressbar=frametitle, sectionpage=none]{metropolis}
\setbeamertemplate{bibliography item}[text]
\setbeamertemplate{frametitle continuation}{}
\setbeamertemplate{section in toc}[numbered titles]
\setbeamertemplate{subsection in toc}[indented titles]

@@

@@

  \begin{frame}
    \frametitle{Possible conflicts}
    \small

@@

    \vfill
    \begin{tabular}{c | c c c c | c c c c}
      & \multicolumn{4}{c|}{\textbf{Safety}} & \multicolumn{4}{|c}{\textbf{Liveness}} \tabularnewline
      \diagbox[dir=NW,width=7em]{within}{using} & atoms & refs & agents & channels & atoms & refs & agents & channels \tabularnewline
      \hline
      atoms & \n & \n & \n & \n & \y & \y & \y & \n \tabularnewline
      refs & \n & \y & \y & \n & \y & \y & \y & \n \tabularnewline
      agents & \y & \y & \y & \y & \y & \y & \y & \n \tabularnewline
      channels & \y & \y & \y & \y & \y & \y & \n & \n \tabularnewline
    \end{tabular}
    \vfill
    \begin{itemize}
      \onslide<2->{
        \item A model reexecutes code that performs an irrevocable action.
      }
      \onslide<3->{
        \item A model reexecutes code that causes the reexecution to continually happen.
      }
      \onslide<4->{
        \item A model that supports blocking operations is used within a model that doesn't.
      }
      \onslide<5->{
        \item A model does not guarantee safety or liveness by design.
      }
    \end{itemize}
  \end{frame}
